%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\newcommand{\emailaddress}{aarya.bhatia1678@gmail.com}
\newcommand{\phonenumber}{217-953-2047}
\newcommand{\address}{Champaign, IL}

\begin{center}
    \textbf{\Huge \scshape Aarya Bhatia} \\ \vspace{1pt}
    \small \phonenumber $|$ 
    \href{mailto:\emailaddress}{\underline{\emailaddress}} $|$ 
    \href{https://github.com/aarya-bhatia}{\underline{github.com/aarya-bhatia}} $|$
    \small \address
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois}{Urbana-Champaign, IL}
      {Bachelor of Science in Applied Mathematics, Minor in Computer Science}{Aug 2020 -- May 2024}

    \resumeItemListStart
    \resumeItem{GPA: 3.7}
    \resumeItem{The Dean's List: Spring 2022}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, Go, SQL, Bash, LaTex, Java, JavaScript} \\
     \textbf{Frameworks}{: MongoDB, Node.js, Flask, Numpy, SFML, REST, OOP } \\
     \textbf{Tools}{: Linux, Git, Vim, Docker, AWS (S3, EC2), Postman, Grafana, Heroku, VS Code } \\
     \textbf{Interests}{: Backend, Problem Solving, Software Testing, Automation, Systems and Networking } \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % \resumeSubheading
    %   {SDE Intern}{May 2023 -- Aug 2023}
    %   {Amazon}{San Fransisco, IL}

    \resumeSubheading
      {Course Assistant, CS 340: Introduction to Computer System}{Aug 2022 -- Present}
      {University of Illinois}{Champaign, IL}
      \resumeItemListStart
        \resumeItem{Tutored 500+ students on system concepts and programming assignments in C and Python.}
        \resumeItem{Developed autograded and randomised questions on the Prairie Learn LMS}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Jan 2023 -- May 2023}
      {University of Illinois}{Champaign, IL}
      \resumeItemListStart
        \resumeItem{Worked with Dr. Angrave Lawrence on a research project to make education more accessible.}
        \resumeItem{Implemented a glossary system for I-Notes, a text-based format of video lectures generated by video captions.}
      \resumeItemListEnd


    \resumeSubheading
      {DevOps Intern}{Jun 2022 -- Aug 2022}
      {Humantic AI}{Gurugram, India}
      \resumeItemListStart
        \resumeItem{Developed a Grafana monitoring dashboards with customized alerts on Email and Slack.}
        \resumeItem{Implemented a stand-alone Python plugin to expose application metrics to Prometheus.}
        \resumeItem{Developed shell script for continuous integration with Jenkins to deploy code on a remote server.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Mar 2022 -- Dec 2022}
      {University of Illinois}{Champaign, IL}
      \resumeItemListStart
        \resumeItem{Develop custom WordPress themes and API with PHP for CyberGIS project websites}
        \resumeItem{Implemented Python scripts for automated testing of Jupyter notebooks on CyberGIS infrastructure.}
        \resumeItem{Implemented a web-based calendar in PHP and integrated it with the Google Calendar.}
      \resumeItemListEnd

    \resumeSubheading
      {Full-Stack Web Developer}{May 2021 -- Aug 2021}
      {Aspire Impact}{Gurugram, India}
      \resumeItemListStart
        \resumeItem{Developed script to analyze survey responses to online behavioral assessments.}
        \resumeItem{Developed a full-stack website with Node JS for online assessments and report generation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{CS 438, Communication Networks Project} $|$ \emph{C}}{Jan 2023 -- Mar 2023}
    \resumeItemListStart
    \resumeItem{Implemented a high-performance polling-based 
    server and a multithreaded client CLI program following the \emph{Inter Relay Chat} network protocol 
    using the RFC 1459 specification, in pure C language.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{CS 340, Intro to Computer Systems Project} $|$ \emph{Python, Flask}}{Mar -- May 2022}
    \resumeItemListStart
    \resumeItem{Implemented a microservice to generate and encode a random maze using Kruskal’s disjoint set algorithm.}
    \resumeItem{Developed a middleware, caching, and validation services to manage many maze-generation servers.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{CS 225, Data Structures Project} $|$ \emph{C++}}{Dec 2021}
    \resumeItemListStart
    \resumeItem{Parsed the Open Flight airport dataset to construct a graph data structure using C++ class templates.}
    \resumeItem{Implemented various algorithms such as BFS, DFS, Page Rank, Dijkstra and Kosaraju’s algorithm to find optimal
    flight paths between airports, rank the airports by importance and discover the strongly connected components.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
